Outstanding Title

### 2017-04-19 writing/EpiDraft.Rmd
Code data scrape

```{r}
#scrape just the New York City value for week 14 of 2017 from cdc website:
library(rvest)
url <- read_html("https://wonder.cdc.gov/mmwr/mmwr_2017.asp?mmwr_year=2017&mmwr_week=14&mmwr_table=2J&request=Submit&mmwr_location=")
#Used Selector Gadget to get css selector
nyc <- html_nodes(url, 'tr:nth-child(15) td:nth-child(2)')
as.numeric(html_text(nyc))

@@

#There was no table for week 2 so we have an NA.
```

>>>>

```{r, cache=T}
#scrape just the New York City value for week 14 of 2017 from cdc website:
library(rvest)
url <- read_html("https://wonder.cdc.gov/mmwr/mmwr_2017.asp?mmwr_year=2017&mmwr_week=14&mmwr_table=2J&request=Submit&mmwr_location=")
#Used Selector Gadget to get css selector
nyc <- html_nodes(url, 'tr:nth-child(15) td:nth-child(2)')
as.numeric(html_text(nyc))

@@

#All in one?
allinone <- i %>% map(~paste("https://wonder.cdc.gov/mmwr/mmwr_2017.asp?mmwr_year=2017&mmwr_week=0", as.character(.x), "&mmwr_table=2J&request=Submit&mmwr_location=", sep="")) %>% map(~read_html(.x)) %>% map(~html_nodes(.x, 'tr:nth-child(15) td:nth-child(2)')) %>% map(~html_text(.x))

#There was no table for week 2 so we have an NA.

#Get ALL THE DATA for NYC 1998-2017 (nothing for 1996 or 7)
#1998:
i <- 1:9
url1to9 <- i %>% map(~paste("https://wonder.cdc.gov/mmwr/mmwr_1995_2014.asp?mmwr_year=1998&mmwr_week=0", as.character(.x), "&mmwr_table=2B&request=Submit&mmwr_location=", sep=""))
i <- 10:53
url10to53 <- i %>% map(~paste("https://wonder.cdc.gov/mmwr/mmwr_1995_2014.asp?mmwr_year=1998&mmwr_week=", as.character(.x), "&mmwr_table=2B&request=Submit&mmwr_location=", sep=""))
url1998 <- c(url1to9, url10to53)
nyc1998 <- url1998 %>% map(~read_html(.x)) %>% map(~html_nodes(.x, 'tr:nth-child(13) td:nth-child(2)')) %>% map(~html_text(.x))
as.numeric(nyc1998)

#For the earlier years we only have cumulative data.  Could take differences via code? 2006 is the first year with variable for current week.

```
